---
title: "LAB 06_05_18"
output: html_notebook
---
```{r}
library(tidyverse)
```
```{r}
?read_csv
```
```{r}
write_cars <- as.data.frame(mtcars) 
write_csv(write_cars, path = "cars.csv")
```
```{r}
read_csv("cars.csv")
```
```{r}
install.packages("readxl")
```
```{r}
library(readxl)
```
```{r}
readxl_example("deaths.xls")
```
```{r}
?read_excel()
```
```{r}
xl_example <- readxl_example("deaths.xls")
xls_example <- readxl_example("deaths.xlsx")
read_excel(xl_example)
```
```{r}
read_excel(xls_example)
```
```{r}
read_excel(xls_example, skip = 4)
```
```{r}
excel_sheets(xl_example)
```
```{r}
install.packages("writexl")
```
```{r}
library(writexl)
```
```{r}  
write_xlsx(mtcars, path= 'cars.xlsx')
```

## Exercises
1.What functions would you use to read a file where feilds were seperated with |? 
    +read.table()
    
2.Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

3.What are the most important arguments to read_fwf()?

## Open Miami-Dade Data Lab

```{r}
service_data <- read_csv("311_Service_Requests_-_Miami-Dade_County.csv")
```
```{r}
install.packages("janitor")
```
```{r}
library(janitor)
```
```{r}
colnames(service_data)
```
```{r}
service_data <- clean_names(service_data)
```
```{r}
colnames(service_data)
```
## Questions
  1.How many rows and columns are in this data?
  ROWS: 657544 COLUMNS: 23
```{r}
dim(service_data)
```
  2.How many cities are represented in the data?
```{r}
library(Hmisc)
```
```{r}
describe(service_data$city)
```
```{r}
unique(service_data$city)
```
How many cities are represented in the data? 
    + 37 (as shown in the table above)

What is the most frequently occuring issue type? Hint: Use the table function.
**PET ACCOUNT UPDATE  55455**

```{r}
table(service_data$issue_type)
```

```{r}
ticket_status<-as.data.frame(service_data$ticket_status)
```
```{r}
library(Hmisc)
```
```{r}
describe(service_data$ticket_status)
```
## What percentage of tickets have a status of ‘CLOSED’? 
= 9.6 percent 
```{r}
tickets <- table(service_data$ticket_status) %>%
  as.data.frame()
```
```{r}
colnames(tickets) <- c('Status', 'Count')
```
```{r}
colnames(tickets)
```
```{r}
tickets$Count
```

```{r}
tickets$Percentage <- tickets$Count / sum(tickets$Count)
```
```{r}
tickets
```
```{r}
write_csv(tickets, path = "ticket_status.csv")
```

## The Meat 

```{r}
library(Hmisc)
```
```{r}
library(tidyverse)
```
```{r}

```


You’re going to leave your work documented in an R Notebook so that you can share it with your team and they can build on it as needed.

Make sure your variables related to Dates are Date data types. If they aren’t, convert them to dates with the format month/day/year.

1. Create a new variable, open_30, with only tickets that are OPEN and were created more than 30 days ago.









